




\begin{thebibliography}{10}

\bibitem{1}
J. L. Ba, J. R. Kiros, and G. E. Hinton, ``Layer Normalization,''
2016.

\bibitem{2}
D. Banerjee, K. Dasgupta, D. Ganguly, and K. Chatterjee, ``A Survey of Offline Handwriting Signature Recognition,''
Mar. 2019.

\bibitem{3}
A. Bhatawdekar, S. Bhattacharya, R. Khatri, and R. Tiwari, ``BHSig260: A Dataset for Offline Signature Verification,''
2020.

\bibitem{4}
A. Dosovitskiy et al., ``An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale,'' {\em in Proceedings of the International Conference on Learning Representations (ICLR)},
2021.

\bibitem{5}
R. O. Duda, P. E. Hart, and D. G. Stork, ``Pattern Classification,'' {\em 2nd ed. Wiley-Interscience},
2000.

\bibitem{6}
T. Fawcett, ``An Introduction to ROC Analysis,'' vol. 27.
2006.

\bibitem{7}
M. A. Ferrer, J. B. Alonso, and C. M. Travieso, ``Offline Geometric Parameters for Automatic Signature Verification Using Fixed-Point Arithmetic,'' {\em IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 27, no. 6, pp. 993--997,
2005.

\bibitem{8}
I. Goodfellow, Y. Bengio, and A. Courville, ``Deep Learning. MIT Press,''
2016.

\bibitem{9}
H. Li S. Zhang and M. Ouyang, ``Multimodal Signature Verification via Hybrid CNN-Transformer Networks,'' {\em in IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)},
Jun. 2023, pp. 11230--11239.

\bibitem{10}
R. Hadsell, S. Chopra, and Y. LeCun, ``Dimensionality Reduction by Learning an Invariant Mapping,'' {\em in Proceedings of the IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR)},
2006, pp. 1735--1742.

\bibitem{11}
L. G. Hafemann, R. Sabourin, and L. S. Oliveira, ``Learning features for offline handwritten signature verification using deep convolutional neural networks,'' {\em Pattern Recognition}, vol. 70, pp. 163--176,
2017

\bibitem{12}
L. G. Hafemann, R. Sabourin, and L. S. Oliveira, ``Offline handwritten signature verification — Literature review,'' {\em in 2017 Seventh International Conference on Image Processing Theory, Tools and Applications (IPTA)},
Nov. 2017, pp. 1--8.

\bibitem{13}
K. He, G. Gkioxari, P. Dollár, and R. Girshick, ``Mask R-CNN,'' {\em IEEE International Conference on Computer Vision (ICCV)}, pp. 2980--2988,
2017.

\bibitem{14}
K. He, X. Zhang, S. Ren, and J. Sun, ``Deep Residual Learning for Image Recognition,'' {\em in Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},
2016, pp. 770--778.

\bibitem{15}
D. Hendrycks and K. Gimpel, ``Gaussian Error Linear Units (GELUs),''
2016.

\bibitem{16}
S. Ioffe and C. Szegedy, ``Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift,'' {\em in Proc. 32nd International Conference on Machine Learning (ICML)},
2015, pp. 448--456.

\bibitem{17}
E. J. R. Justino, F. Bortolozzi, and R. Sabourin, ``A comparison of SVM and HMM classifiers in the off-line signature verification,'' {\em Pattern Recognition Letters}, vol. 26, no. 9, pp. 1377--1385,
2005.

\bibitem{18}
R. G. Keys, ``Cubic Convolution Interpolation for Digital Image Processing,'' vol. 29,
1981.

\bibitem{19}
A. Krizhevsky, I. Sutskever, and G. E. Hinton, ``ImageNet classification with deep convolutional neural networks,'' {\em in Proceedings of the 25th International Conference on Neural Information Processing Systems (NIPS)}, Curran Associates Inc.,
2012, pp. 1097--1105.

\bibitem{20}
L. L. Lee, T. Berger, and E. Aviczer, ``Reliable on-line human signature verification systems,'' {\em IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 18, no. 6, pp. 643--647,
Jun. 1996.

\bibitem{21}
C. Li, F. Lin, Z. Wang, C. Yu, L. Yuan, and H. Wang, ``Deephsv: User-independent offline signature verification using two-channel CNN,'' {\em in International Conference on Document Analysis and Recognition (ICDAR)},
2019.

\bibitem{22}
M. Lin, Q. Chen, and S. Yan, ``Network In Network,'' {\em in Proc. International Conference on Learning Representations (ICLR)},
2014.

\bibitem{23}
T. Lin, P. Dollár, R. Girshick, K. He, B. Hariharan, and S. Belongie, ``Feature Pyramid Networks for Object Detection,'' {\em IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 936--944,
2017.

\bibitem{24}
Z. Liu et al., ``Swin Transformer: Hierarchical Vision Transformer using Shifted Windows,'' {\em in Proc. IEEE International Conference on Computer Vision (ICCV)},
2021, pp. 10012--10022.

\bibitem{25}
X. Lu, L. Huang, and F. Yin, ``Cut and Compare: End-to-End Offline Signature Verification Network,'' {\em in Proceedings of the 25th International Conference on Pattern Recognition (ICPR)},
2021, pp. 176--183.

\bibitem{26}
T. M. Mitchell, ``Machine Learning.'' {\em McGraw-Hill},
1997.

\bibitem{27}
R. K. Mohapatra, K. Shaswat, and S. Kedia, ``Offline handwritten signature verification using CNN inspired by inception V1 architecture,'' {\em in 2019 Fifth International Conference on Image Information Processing (ICIIP)},
2019, pp. 263--267.

\bibitem{28}
Y. Muhtar, W. Kang, A. Rexit, Mahpirat, and K. Ubul, ``A Survey of Offline Handwritten Signature Verification Based on Deep Learning,'' {\em in 2022 3rd International Conference on Pattern Recognition and Machine Learning (PRML)},
Jul. 2022, pp. 391--397.

\bibitem{29}
V. Nair and G. E. Hinton, ``Rectified Linear Units Improve Restricted Boltzmann Machines,'' {\em Proc. 27th International Conference on Machine Learning (ICML)}, pp. 807--814,
2010.

\bibitem{30}
S. Pankanti, S. Prabhakar, and A. K. Jain, ``Cedar: A database of handwritten signatures for benchmarking signature verification systems,'' {\em in Proceedings of the IEEE International Conference on Image Processing (ICIP)},
2000, pp. 5--8.

\bibitem{31}
R. Plamondon and G. Lorette, ``Automatic signature verification and writer identification—The state of the art,'' {\em Pattern Recognition}, vol. 22, no. 2, pp. 107--131,
1989.

\bibitem{32}
S. Dey, A. Dutta and J. I. Toledo, ``Signet: A Deep Learning Architecture for Offline Signature Verification Using Multi-Scale CNN and SVM,'' {\em IEEE Access}, vol. 8, pp. 118942--118956,
2020.

\bibitem{33}
A. Shrivastava, A. Gupta, and R. Girshick, ``Training Region-based Object Detectors with Online Hard Example Mining,'' {\em in Proc. IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},
2016, pp. 761--769.

\bibitem{34}
K. Simonyan and A. Zisserman, ``Very deep convolutional networks for large-scale image recognition,'' {\em in Proceedings of the International Conference on Learning Representations (ICLR)},
2015.

\bibitem{35}
J. F. Vargas, M. A. Ferrer, C. M. Travieso, and J. B. Alonso, ``Off-line Handwritten Signature GPDS-960 Corpus,'' {\em in Proc. 9th International Conference on Document Analysis and Recognition (ICDAR)},
2007, pp. 764--768.

\bibitem{36}
A. Vaswani et al., ``Attention is All You Need,'' {\em in Advances in Neural Information Processing Systems (NeurIPS)},
2017, pp. 5998--6008.

\bibitem{37}
M. Wang, S. Lu, D. Zhu, and J. Lin, ``A High-Speed and Low-Complexity Architecture for Softmax Function in Deep Learning,'' {\em in 2018 IEEE Asia Pacific Conference on Circuits and Systems (APCCAS)}, Chengdu, China: IEEE,
2018, pp. 223--226.

\bibitem{38}
P. Wei, H. Li, and P. Hu, ``Inverse discriminative networks for handwritten signature verification,'' {\em in The IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},
2019.

\bibitem{39}
X. Wang Y. Chen, Z. Liu and L. Jin, ``Vision Transformer for Offline Handwritten Signature Verification,'' {\em IEEE Transactions on Biometrics, Behavior, and Identity Science}, vol. 4, no. 3, pp. 450--465,
Jul. 2022.

\bibitem{40}
M. H. M. Yusof and V. K. Madasu, ``Signature Verification and Forgery Detection System,'' {\em in Proc. Student Conference on Research and Development (SCORED 2003)},
2003, pp. 9--14.

\bibitem{41}
Y. Zhang et al., ``TransOSV: Offline Signature Verification with Transformers,'' {\em in Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},
2023.


\end{thebibliography}



























